---
title: "cava: Batch-effect adjusted Simon’s two-stage design "
author: "Chenguang Wang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cava: Batch-effect adjusted Simon’s two-stage design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Installation

The package **cava** can be installed directly from *CRAN*: 
```{r, eval = FALSE, echo = TRUE}
install.packages("cava");
```
Some packages (e.g., *shiny*) are required to run the graphical user interface for *visit***, 
but are not required to run **cava** through a *R* terminal.

```{r, eval = TRUE, echo = FALSE, message = FALSE}
require(cava);
set.seed(10000);
```

# Introduction

This is a clinical trial design software suite for cancer vaccines.
The package currently includes two major designs for cancer vaccine clinical
trials. The fist design is a Bayesian Phase I trial design that allows
simultaneous evaluation of safety and immunogenicity outcomes in the context
of vaccine studies. See Wang (2019) <DOI:10.1002/sim.8021> for the details
of the Phase I cancer vaccine trial design. The second design is a
batch-effect adjusted Simon two-stage design. This package's focus is the 
addition of batch-effect adjusted Simon two-stage design, where batch-effect
is accounted for. 

# Conduct Simulation and Designs

## baSimuBetaBin
Simulate batch data from Beta-Binomial with the given parameters. 
```{r, eval = TRUE, echo = FALSE, message = TRUE}
baSimuBetaBin(4, 0.2, rho = 0.5);
```

## baDesignBetaBin
Get designs from BetaBinomial designs with given parameters. 
```{r, eval = TRUE, echo = FALSE, message = TRUE}

par.design <-  NULL;
par.design$P0 <- 0.2;
par.design$P1 <- 0.4;
par.design$ALPHA <- 0.5;
par.design$POWER <- 0.5;

baDesignBetaBin(par.design, rho = 1, bsizes = 2, nmin = 10, nmax = 20)
```


# Graphical User Interface (GUI)

The **cava** package provides a web-based GUI for composite endpoint analysis. 
The GUI includes both **cava** and **visit** packages. The GUI can be accessed by

```{r, echo=TRUE, eval=FALSE}
cvShiny();
```